Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-20 krs-survey.tex
Removed DyKnow from reviewed system + mentionned Heintz survey
DyKnow has been removed because no focus on 'service robot'/'human environment' + a bit too lowlevel

@@

However, several authors from fields that are connected to the robotics have
previously listed desirable features of artificial systems aiming at cognitive
abilities as rich as possible.

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMRKF & & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe/?mid=symbolic_reasoning} & ? & Horn Clauses & ? & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

%%%%%%%%%% Underlying knowledge model table %%%%%%%%
\begin{table}
\begin{center}
\rowcolors{2}{lightgray}{codegray}

\begin{tabular}{lp{4cm}}
\hiderowcolors
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

\begin{tabular}{cp{4.5cm}ccccccccc}
\toprule
\multicolumn{2}{c}{\bf Category} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} & {\sc DY-KNOW} \\

@@

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses & \\
 & Expressive power & & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) & \\
 & Meta-cognition & ++ & ++ & & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++ &  \\
 & Representation of temporality & & & & & & & & + &  \\
 & Context & & & & & & & & ++ &  \\
 & Alternative worlds & & +++ & & & & & & &  \\
 & Introspection & + (SRDF) & & & & & & & &  \\
 & Memory & & + & & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & &  \\
 & Knowledge structure alteration & & ++ & & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & & & & \\
 & Non-monotonic reasoning & & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & &  \\
 & Prediction, projection, diagnosis & & & & & & & & &  \\
 & Physics-based reasoning & +++ (extension) & & & & & & & &  \\
 & Planning & + & +++ (external module) & & & & & & &  \\
 & Learning & & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & &  \\
 & Grounding & & & & & & & & &  \\
 & Instanciation & & & & & & & & &  \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & & &  \\
 & ...with executive layers & & & & & & & & &  \\
 & Monitoring and debugging & & & & & & & & &  \\
 & Performances & & & & & & & & &  \\

>>>>

This exclude \textit{de-facto} platforms like {\sc DyKnow}~\cite{Heintz2004}
which are focused on data fusion and knowledge grounding at lower levels.

@@

In a slightly broader context, Heintz et al.~\cite{Heintz2008} define
\emph{knowledge processing middlewares} as systems supporting ``declarative
specifications for flexible configuration and dynamic reconfiguration of
context dependent processing at many different levels of abstraction''. They
identify six characteristics: the system must be able to merge informations
from different, possibly distributed sources; it should support quantitative as
well as qualitative processing of information, it should offer bottom-up and
top-down processing, it should be able to deal with uncertainty, allow for
``flexible configuration and reconfiguration'' (which require what we call
\emph{non-monotonicity} in this article) and eventually Heintz et al. call for
meta-knowledge and introspective capacities (``declarative specification of the
processing functionalities''). In this paper, we focus our analysis on similar
system with however an emphazise on the symbolic capabilities.

At a broader scope, several authors from fields that are connected to robotics
have previously listed desirable features of artificial systems aiming at
cognitive abilities as rich as possible.

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMRKF & & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe/?mid=symbolic_reasoning} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

%%%%%%%%%% Underlying knowledge model table %%%%%%%%
\begin{table}
\begin{center}

\begin{tabular}{lp{4cm}}
\toprule
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\midrule
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

\begin{tabular}{cp{4.5cm}ccccccccc}
\toprule
\multicolumn{2}{c}{\bf Category} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} \\

@@

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses \\
 & Expressive power & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++  \\
 & Representation of temporality & & & & & & & & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & +  \\
 & Knowledge structure alteration & & ++ & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & & & \\
 & Non-monotonic reasoning & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external module) & & & & & & + \\
 & Learning & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & & & & & & & & ++ \\
 & Instanciation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & & ++ \\
 & ...with executive layers & & & & & & & & ++ \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & & & & \\
